|

### 2021-05-25 article/article.Rmd
draft methods section, add ref chen, cheung

---
title:  |
        | The Effect of Legislature Size on Public Spending
        | A Meta-Analysis
author: 
  - Huzeyfe Alptekin[^huzeyfe]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
  - Catarina Roman[^catarina]
date: \today
thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at <https://github.com/danilofreire/distributive-politics-meta-analysis>. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the \"law of $1/n$\" and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending. Based on a sample of 29 articles, we find no robust evidence for the effect of legislature size on government budgets. Yet the aggregate results show significant heterogeneity. While earlier studies provide moderate support for the \"law of $1/n$\", papers using causal inference methods consistently find a negative relationship between seats and spending. The available evidence also indicates that proportional representation and mixed voting systems are no more likely to overspend than majoritarian ones."
abstractspacing: double
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

@@

[^danilo]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.

@@

[^catarina]: Research Associate, School of International Relations, Fundação Getulio Vargas, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

@@

# Methods

We collected the study sample using three criteria. First, the study should
cite \citet{weingast1981political} as their work is foundational to the
distributive politics literature. Second, the study had to use quantitative
methods to estimate the relationship between our variables of
interest.\footnote{As meta-analysis requires a single estimate per observation,
we excluded articles that use interaction terms or quadratic specifications of
our independent variables.} Third, the study should be written in the English
language. We conducted a primary search using Scopus, Microsoft Academic, and
Google Scholar, three large academic databases.\footnote{See the Supplementary
Material for code.}

After applying our exclusion criteria, the search produced a dataset of 
`r length(unique(dat$id))` studies as of the 21\textsuperscript{st} of November,
2019. Table \ref{tab:papers} contains the full list of articles from which we
drew data. A PRISMA\footnote{The Preferred Reporting Items for Systematic
Reviews and Meta-Analyses (PRISMA) statement provides a checklist designed
to improve the quality and transparency of study selection processes in
meta-analyses. For more information on the PRISMA framework, see
\citet{liberati2009prisma}.} flow diagram showing the number of resulting
papers after each review step is available in the Supplementary Material.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.4cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
\tabularnewline
\midrule
\endhead
```{r, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authorCite, title, journalCode, year, locationISO, method, elecsys3) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authorCite[i]), ' & ', aux$title[i], ' & ',
      aux$journalCode[i], ' & ', aux$year[i], ' & ', 
      aux$locationISO[i], ' & ', aux$method[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal,
OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
NM$=$Non-majoritarian (mixed or proportional representation). Country codes
follow the ISO 3166-1 alpha-3 international standard.} \end{minipage}
\end{longtable}

@@

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Five articles use cross-national data and analyse from 2 to 110
countries. Early studies used OLS and panel data methods to estimate the
results, whereas the use of regression discontinuity designs is a recent
addition to the literature, as the first paper to apply it was published in 2012.

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
suggested by \citet{weingast1981political} and tested the impact of larger
legislatures on different measures of government spending. Our independent
variables of interest are $n$, lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), ($\log(n)$), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and $k$, which represents upper chamber
size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).

We also coded four moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study ($n$,
log($n$), or $k$). The additional moderators are: 1) publication year; 2) paper
publication in an academic journal; 3) electoral system; 4) estimation method.
Since the literature on the "law of $1/n$" is notably diverse, we were
restricted to include only the moderators that either refer to important
theoretical questions, such as the effect of the electoral system on public
spending, or to essential characteristics of the publications themselves.
Although more moderators exist in the literature (ie., data aggregation level),
they do not appear as often as required for the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

@@

```{r, echo = FALSE, results='hide', warning=FALSE, message=FALSE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
fulldat$usemeta2 <- as.character(fulldat$usemeta2)
fulldat$usemeta2 <- factor(fulldat$usemeta2)
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method)

res <- export2latex(
  descrTable(~.-usemeta2, aux, y = aux$usemeta2,
             show.p.overall = F, show.all = T, all.last = T), 
  caption = 'Descriptive statistics of moderators\\label{tab:descriptive}'
)
res <- gsub(pattern = '\\[ALL\\]', 'All Coefficients', res$desc, useBytes = T)
cat(res)
```

\footnotesize
\begin{longtable}{lccc}\caption{Descriptive Statistics of Moderators\label{tab:descriptive}}\\
\hline  
& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
&       N=42        &       N=100        &    N=142    \\
\hline
\hline     
\endfirsthead 
\multicolumn{4}{l}{\tablename\ \thetable{} \textit{-- continued from previous page}}\\ 
\hline
& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
&       N=42        &       N=100        &    N=142    \\ 
\hline
\hline  
\endhead   
\hline
\multicolumn{4}{l}{\textit{continued on next page}} \\ 
\endfoot   
\multicolumn{4}{l}{}  \\ 
\endlastfoot 
Independent Variables: &                   &                    &            \\ 
$\qquad$K &    12 (28.6\%)     &     33 (33.0\%)     & 45 (31.7\%) \\ 
$\qquad$N &    24 (57.1\%)     &     55 (55.0\%)     & 79 (55.6\%) \\ 
$\qquad$logN &     6 (14.3\%)     &     12 (12.0\%)     & 18 (12.7\%) \\ 
Year &    2009 (6.56)    &    2008 (5.82)     & 2008 (6.04)\\ 
Published work: &                   &                    &            \\ 
$\qquad$Yes &    36 (85.7\%)     &     93 (93.0\%)     & 129 (90.8\%)\\ 
$\qquad$No &     6 (14.3\%)     &     7 (7.00\%)      & 13 (9.15\%) \\ 
Electoral system: &                   &                    &            \\ 
$\qquad$Majoritarian &    22 (52.4\%)     &     46 (46.0\%)     & 68 (47.9\%) \\ 
$\qquad$Non-Majoritarian &    20 (47.6\%)     &     54 (54.0\%)     & 74 (52.1\%) \\ 
Estimation method: &                   &                    &            \\ 
$\qquad$OLS &    11 (26.2\%)     &     36 (36.0\%)     & 47 (33.1\%) \\ 
$\qquad$PANEL &    23 (54.8\%)     &     51 (51.0\%)     & 74 (52.1\%) \\ 
$\qquad$IV &     5 (11.9\%)     &     7 (7.00\%)      & 12 (8.45\%) \\ 
$\qquad$RDD &     3 (7.14\%)     &     6 (6.00\%)      &  9 (6.34\%)  \\

\hline
\end{longtable}

Since most selected articles have more than one effect size, the observations
in our dataset are not independent. To reduce the impact of multicollinearity,
we estimate the models using two sets of study coefficients. The first group
includes only the most rigorous model from each paper, that is, those estimated
with the largest $n$, most control variables, and fixed effects if the authors
added them. If the article employed a regression discontinuity design, we chose
the coefficient from the optimal bandwidth or from the intermediate one. This
sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
independent variables of interest \citep{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen_malhotra_2007, crowley2019law,
lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
ricciuti2003trading}. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect
sizes reported in the `r length(unique(dat$id))` papers. Here we focus on the results for our restricted
sample as we consider them more robust, but the findings are very similar when
we use the extended set. We discuss eventual differences in the next section.
Please refer to the Supplementary Material for further information about our
sampling process and for the complete results.

# Results

## Binomial Z-Tests
\label{sub:binomial}

The "law of $1/n$" states that more legislators increase government expenditure.
Here we employ three methods to assess the empirical validity of that
relationship. First, we run a binomial one-proportion z-test to determine
whether the study coefficients have a positive or negative sign. Then, we fit 9
random-effect models using the \texttt{meta} \citep{balduzzi2019perform} and the
\texttt{dmetar} \citep{dmetar2019} packages for the \texttt{R} statistical
language \citep{rstats2019}. We estimate the true effect size variance
($\tau^2$) with a Restricted Maximum Likelihood Estimator, which the literature
considers the most precise for continuous dependent variables
\citep{veroniki2016methods}. Lastly, we run a series of meta-regressions to test
possible sources of result heterogeneity. To recapitulate, our independent
variables of interest are lower chamber size ($n$), the natural logarithm of
lower chamber size (log($n$)), and upper chamber size ($k$). The dependent
variables are public expenditure per capita, the natural logarithm of public
expenditure per capita, and government expenditure as a percentage of GDP. Since
the outcomes have different scales, we treat them separately in our models.

```{r, cache=TRUE, echo = FALSE}
aux <- filter(dat, indepvar2 == "N")
binN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
aux <- filter(dat, indepvar2=='K')
binK <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
aux <- filter(dat, indepvar2 == "logN")
binlogN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
```

The binomial z-test evaluates whether the coefficient of our independent
variables are positive or negative. The null hypothesis here states that the
sign of the coefficient is equally likely to be positive or negative. We start
with $n$, lower house size. Our results indicate that there is no correlation
between the number of legislators in the lower house and public expenditure 
(successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
association between both. The binomial test for log($n$) also shows a
non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
positive result for the number of legislators in the upper house ($k$), which is
in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
$p$-value = `r round(as.numeric(binK$p.value), 3)`).

## Meta-Analysis
\label{sub:Meta-Analysis}

We then proceed to the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the 9 possible variable combinations, we found only 7 in
the article pool. Our sample includes no papers that analyse the relationships
between log($n$) and public expenditure per capita or between $k$ and the
logarithm of public expenditure per capita.

```{r, echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE}
mod <- list()
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod[[1]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod[[2]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod[[3]] <- metagen(
  coef, SE, data=aux,
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction = TRUE,
  sm="SMD"
  )

# Pooling effects analysis -- logExpPC x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

mod[[4]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Pooling effects analysis -- PCTGDP x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod[[5]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Pooling effects analysis -- PCTGDP x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

mod[[6]] <- metagen(
  coef, SE, data=aux,
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction=TRUE,
  sm="SMD"
  )

# Pooling effects analysis -- PCTGDP x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

mod[[7]] <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

# Full model - Pooling effects analysis -- PCTGDP x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod[[8]] <- metagen(coef, SE, data = aux,
          studlab = paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm = "SMD")

# Full data - Pooling effects analysis -- ExpPC x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

>>>>

---
title:  |
        | The Effect of Legislature Size on Public Spending:
        | A Meta-Analysis
author: 
  - Huzeyfe Alptekin[^huzeyfe]
  - Danilo Freire[^danilo]
  - Umberto Mignozzetti[^umberto]
  - Catarina Roman[^catarina]
date: \today
thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at <https://github.com/danilofreire/distributive-politics-meta-analysis>. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures. Their proposition is currently known as the \"law of $1/n$\" and has been widely debated in political science and public administration. However, recent studies have questioned the validity of the theory. In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending. Based on a sample of 29 articles, we find no robust evidence for the effect of legislature size on government budgets. Yet the aggregate results show significant heterogeneity. While earlier studies provide moderate support for the \"law of $1/n$\", papers using causal inference methods consistently find a negative relationship between seats and spending. The available evidence also indicates that proportional representation and mixed voting systems are no more likely to overspend than majoritarian ones."
abstractspacing: double
keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
jelcodes: H21; H23; H50; H61
fontsize: 11pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
    md_extensions: +raw_attribute
---

@@

[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.

@@

[^catarina]: PhD Student, Department of Political Science, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

@@

# Data and Methods

We compiled our study sample in three rounds. In the first search round, we
gathered data from three large academic databases (Scopus, Microsoft Academic,
and Google Scholar) and looked for studies that cited
\citet{weingast1981political}, as it is the foundational work in the literature
on the "law of $1/n$". We then restricted our query to articles written in
English and, to ensure that studies were comparable, we only included papers
that used quantitative methods to investigate the relationship between
legislature size and public spending\footnote{Please refer to Section C in the
Supplementary Material for a detailed description of the selection procedure.
We include two PRISMA (Preferred Reporting Items for Systematic Reviews and
Meta-Analyses) flow diagrammes \citep{liberati2009prisma} showing the number of
resulting papers after each review step.}. After this stage, we identified the
variables authors most commonly employ to measure government expenditure and
legislature size, our dependent and independent variables, respectively. For
government expenditure, our study sample uses (i) public expenditure as a share
of GDP; (ii) public expenditure per capita; and (iii) the natural logarithm of
public expenditure per capita as its main variables of interest\footnote{Since
meta-analysis requires a single estimate per observation, we excluded articles
that use interaction terms or quadratic specifications of our selected
variables.}. In regards to legislature size, the variables are (i) lower
chamber size; (ii) natural logarithm of lower chamber size; and (iii) upper
house size\footnote{There are a few important nuances concerning coding of
these variables. For instance, unicameralism is captured both by lower chamber
size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the
literature estimates how institutional designs affect this relationship, ours
and many other articles use both lower and upper chamber sizes as main
explanatory variables. We did not find any articles that used the natural
logarithm of upper chamber size.}.

In the second round, we did not require articles to cite @weingast1981political
and used a keyword-based query on Google Scholar to broaden the scope of the
first search. We again restricted the search to articles written in English
which employed quantitative methods. In the third search round, we looked into
the personal webpages of every author we had already included in our previous
sample. The purpose of this manual search was to assess whether there was any
working paper or unpublished manuscript which we might had missed in the
previous queries. All papers we found in that last search had already been
included in our sample. Combined, the three searches produced a dataset of 
`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March,
2021. Table \ref{tab:papers} contains the full list of articles we analyse in
this paper.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead 
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year)
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Journals: Unpub$=$Unpublished, JPE$=$Journal of
Political Economy, EJPE$=$European Journal of Political Economy, PC$=$Public
Choice, JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private
Enterprise, APSR$=$American Political Science Review, SEJ$=$Southern Economic
Journal, UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative
International Development, SSQ$=$Social Science Quarterly, SPPQ$=$State
Politics and Policy Quarterly, CPS$=$Comparative Political Studies,
RivPE$=$Rivista di Politica Economica, E\&P$=$Economics and Politics,
NTJ$=$National Tax Journal. Country codes follow the ISO 3166-1 alpha-3
international standard. Dependent variable: ExpPC$=$Per capita expenditure,
logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as
a percentage of GDP. Method: OLS$=$Ordinary least squares, IV$=$Instrumental
variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity
design. Electoral system: M$=$Majoritarian, NM$=$Non-majoritarian (mixed or
proportional representation).} 
\end{minipage} 
\end{longtable}

@@

Our study sample reflects the development of the literature. Although the "law
of $1/n$" was first formulated in 1981, the empirical assessment of the theory
only started a few years later, as dates of publishing range from `r min(dat$year)`
to `r max(dat$year)`. Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`). Eight articles use cross-national data and analyse from 2 to 110
countries. Early studies used OLS and panel data methods to estimate the
results, while studies from 2012 onward have also applied causal inference designs,
such as instrumental variables and regression discontinuity models.

Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
and tested the impact of larger legislatures on different measures of government
spending. Our independent variables of interest are lower chamber size 
(`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).

We also coded five moderators that may help us understand the heterogeneity in
the reported results. We included them in our meta-regressions alongside an
indicator for the type of independent variable used in the original study. The
additional moderators are: 1) publication year; 2) paper publication in an
academic journal; 3) estimation method; 4) institutional design; 5) electoral
system. Since the literature on the "law of $1/n$" is notably diverse, we
included only moderators that either refer to important theoretical questions,
such as the effect of the electoral system on public spending, or to essential
characteristics of the publications themselves. Although more moderators exist
in the literature (e.g., data aggregation level), they do not appear as often
as necessary for their inclusion in the meta-regressions. Table
\ref{tab:descriptive} shows the descriptive statistics of the moderator
variables.

@@

\footnotesize
```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign) %>%
  rename(`Independent Variables` = indepvar2,
         `Year`                  = year,
         `Published work`        = published,
         `Estimation method`     = method,
         `Institutional Design`  = instdesign,
         `Electoral system`      = elecsys2)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators",
          format  = "latex")
```
\normalsize

A key methodological issue we had to address concerns the potential violation
of an important assumption in a meta-analysis, that of effect size independence
[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
sample, authors frequently use similar datasets, and almost all papers fit more
than one model with similar variables, what suggests that the assumption does
not hold. We use two procedures to tackle this problem. First, we created two
sets of study coefficients to reduce the impact of multicollinearity in our
estimations. The first group includes only the most rigorous models from each
paper, that is, those estimated with the largest $n$, most control variables,
and fixed effects if the authors added them. If the article employed a
regression discontinuity design, we chose the coefficient from the optimal
bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]`
estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed
two dependent or independent variables of interest\footnote{The papers that
used more than one dependent or independent variable of interest are
\citet{baqir1999districts, bjedov2014impact, bradbury2001legislative,
chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal,
lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
ricciuti2003trading, ricciuti2004legislatures}.}. Our second sample, in
contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the 
`r length(unique(dat$id))` papers. Here we focus on the results for our restricted
sample as we consider them more robust, but the findings are very similar when
we use the extended set.

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, one including a unique publication
ID for each paper, and another indicating the data source used in the original
study. By adding these two levels, we account for within- and between-study
variation, thus removing these sources of effect size dependency. More
information about the multilevel models can be found in Section H of the
Supplementary Material.
